{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

            Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of Algorithm \ref{alg:linear-rgmapg}, i.e: $n_{j + k + 1} = p_{j + k}$ for $ 0 \le k \le T_\epsilon - 1$.

        \end{proof}
        \begin{theorem}[bounds on the total iterations]
            ...
        \end{theorem}
        \begin{proof}

>>>>

            Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of Algorithm \ref{alg:linear-rgmapg}, i.e: $n_{t + 1} = p_t$
            for $j \le t \le j + T_\epsilon - 1$, and denote $s = j + T_\epsilon -1$ for better notations, giving us $j \le t \le s$. 
        \begin{theorem}[bounds on the total iterations]
